A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-10 paper/paper.Rnw
Incorporate edits and add brief results outline

In this paper, we discuss an alternate approach that uses an additional model layer to transfer the feature vector output into a vector of probabilities representing the detection of geometric elements in shoe tread images. Working within the feature space used by forensic examiners allows us to augment human-identified features with model output, assessing similarity of different shoe images on a feature set that is explicitly relevant to the domain.
%\svp{Add 1-2 sentences connecting feature sets to the goal of reducing workload - possibly cite solemate as an example of manual feature identification}
In addition, much of the existing software to assess geometric similarity, such as SoleMate\footnote{\url{http://www.fosterfreeman.com/trace-evidence/357-sicar-6-solemate-2.html}}, requires examiners to identify and label features manually; automating classification within the currently used feature space could reduce or eliminate the need for such manual classification.

\section{Materials and Methods}
%\svp{Short bit (1-2 sentences) about low-level feature detectors and why they fail with this problem.}
\mt{Shoeprint evidence from crime scenes is most commonly collected in the form of a photograph, so any useful method to automatically identify outsole characteristics must take the form of an image analysis task.}\svp{We're not working with prints, though - please try to avoid the temptation to delve too far into prints. "Ultimately, most pattern evidence is stored in photographic form; as a result, we must use image analysis methods to create numerical features from the original visual record." or something to that effect.}
There are a number of methods that may be employed to identify shapes and features in an image, such as \svp{Fourier transforms, }Hough transformations \citep{ballardGeneralizingHoughTransform1981} and other low-level feature extraction methods aimed at detecting specific shapes, such as edges, corners, blobs, or ridges \citep[Ch 15]{machineVision}. While these methods are useful in identifying these specific features at a low level, they can be computationally intensive and only identify features on a very small scale; as a result, they cannot reliably identify large geometric shapes like those that may be found in an outsole image.
%\svp{Motivate the use of CNNs directly - complex model, higher level of feature aggregation. Mention pre-trained networks to transition.}
Convolutional neural networks (CNNs) are widely recognized as superior for novel image classification. CNNs are a form of artificial neural network which make use of the image convolution operator used by many low-level feature extraction methods, with the additional ability to aggregate such features and meaningfully connect them to a pre-determined set of labels. CNNs have deep architectures that can be trained to identify complex patterns, but they are structurally similar to the \svp{architecture of the }human visual \svp{system} and output binary or probabilistic predictions for given labels that are readily interpretable. As CNNs make use of labeled training data, the predictions generated are for features which are similar to those identified by humans, resulting in models with greater face validity. Once a CNN is trained, it is relatively fast and easy to apply the model to new images and obtain classifications.

@@

Many convolutional neural networks have been trained on a set of images known as ImageNet; these images are hierarchically labeled, so the same image of a dog may have labels of sky, grass, and trees, and the dog may be labeled as ``mammal'', ``dog'', ``retriever'', and ``golden retriever'' at increasing levels of label complexity \citep{dengImageNetLargeScaleHierarchical}. CNNs trained on ImageNet are optimized for general human-like vision, that is, the ability to recognize a large set of different features simultaneously. As a result, the base of networks trained on these sets are often used for transfer learning, because the initial layers are broadly generalizable to a wide variety of more specific image labeling tasks. \svp{You need to talk about the model structure of vgg16 before you start talking about layers. Talk of convolutional blocks doesn't really make sense until you show the layer structure.}\autoref{fig:vgg16layers} shows a selection of filters from VGG16, where each filter detects the presence of specific shapes and colors. Each row of filters in \autoref{fig:vgg16layers} corresponds to one of the five convolutional blocks of VGG16. Filters in earlier convolutional blocks detect simple features, such as colors and blobs, while later filters detect more complex combinations of features. Each of the five convolutional blocks has between 128 and 1,536 filters, and a single image is made up of some combination of the thousands of features that are detected by those filters.

@@

<<vgg16layers, fig.width = 7, fig.height = 5.75, fig.cap = "A selection of filters from the convolutional layers of VGG16.\\svp{Label the rows with block numbers please}">>=
imgs <- list.files("./images/vgg16layers/", recursive = T, full.names = T)
pngs <- lapply(imgs, function(x) png::readPNG(x)[46:1596, 32:1582, ])
grobs <- lapply(pngs, grid::rasterGrob)
gridExtra::grid.arrange(grobs = grobs, nrow = 5)
@

@@

The categories we use in this study are operationally defined as follows:
\begin{description}
\item [Bowtie] Bowtie shapes are roughly quadrilateral, with two opposite concave faces. The remaining two faces can be convex or straight, and the concave faces may have straight portions, so long as there is a concave region. %Using this definition, shapes such as butterflies are included as bowties. \svp{I'm still on the fence - we can just not mention this, or we could move butterflies to "star"...} \mt{I think it makes a lot of sense to move them to star. That means redoing the poster/slides examples though... grrrrrr} I'm just commenting that bit out for now.
\item [Chevron] Chevron shapes include repeating parallel lines as well as individual ``v" shapes. They may be angular but can also be curved.
\item [Circle] Circles include ellipses and ovals; they must be round.
\item [Line] Lines are repeated and parallel; a more general definition of a line would be difficult to differentiate from many other patterns. Lines can be mildly curved.
\item [Polygon] Polygons are defined in this standard to have more than 4 sides. They include pentagons, hexagons, and octagons.
\item [Quadrilateral] Quadrilaterals (quads) have four sides. They may have rounded or square corners.
\item [Star] Stars are any shape with alternating concave and convex regions, or lines which emanate from a central point. ``X" and ``+" shapes are also classified as stars.
\item [Text] Text is any shape which would be identified as text by a reasonable human. In most cases, the text on the outsole images used is made up of Latin alphabet characters; the model will likely not recognize text in other scripts (but could be trained if non-Latin text images could be obtained).
\item [Triangle] Triangles are any three-sided figure. Like quadrilaterals, they can have rounded corners. In some cases, it is difficult to distinguish between a trapezoidal shape and a triangle when rounded corners are involved.
\item [Other] Other features which were marked include logos, various textures (including crepe, stippling, etc.), and smooth regions with no discernible features. These regions are grouped and provide additional information - that none of the previous nine categories are present.
\end{description}

@@

%Labeled images are scarce relative to the amount of data necessary to train a neural network.
Although transfer learning substantially reduces the amount of data required to train a CNN \svp{by several orders of magnitude}, \fix{labeled images are still difficult or time-consuming to generate relative to the amount of data necessary to train even a small neural network adequately. Another common solution to data scarcity is to artificially enlarge the data set using a process called image augmentation \citep{krizhevskyImageNetClassificationDeep2012}.} \svp{I would lose the last clause of the first sentence and combine it with the next, e.g. to make most efficient use of the labeled data, we enlarge the training data using a process called image augmentation.}
 Augmentation is the transformation of original input data using image operations such as cropping, zoom, skew, rotation, and color balance modification in order to distort or alter the image while maintaining the essential features corresponding to the label. This process reduces the potential for overfitting the model to the specific set of image data used during the training process, and also increases the amount of data available for training. Examples of pre- and post-augmentation images are shown in \autoref{fig:augmented}.

@@

The \Sexpr{nrow(dfunion)} images were split such that 60\% were used for training. Since \mt{some categories are much more common than others,}\svp{I like the equal proportion phrasing better myself}
%the categories do not exist in equal proportion in the labeled data,
the training data were weighted by proportion during the training process to \svp{ensure that the model can identify both rare and common geometric shapes}.%from being overwhelmed by more frequent categories.
Of the remaining 40\% of data, half were used for validation, to monitor the training process, and the remaining data were for testing the performance of the fitted model.

@@

\autoref{fig:training-accuracy} shows the training and validation accuracy and loss at each epoch of the fitting process. Overfitting occurs when a model learns the training data so well that its understanding of the categories becomes specific to the training cases, which, in turn, leads to poor prediction of new images that were not in the training set.
%Overfitting, or fitting a model which performs too well on the training data relative to the validation data,
\svp{get rid of passive voice here. Overfitting occurs when the validation loss begins to increase after reaching a global minimum} Overfitting is suspected if the validation loss starts to increase after reaching a global minimum. Alternately, underfitting occurs if the validation accuracy is still increasing when model optimization is terminated\svp{(for instance, between epochs 1 and 10 in \autoref{fig:training-accuracy})}, because model performance is still improving with continued training. \svp{In \autoref{fig:training-accuracy}, validation accuracy levels off after epoch 20, and validation loss has not yet begun to increase at epoch 30,} indicating that the model optimization process was halted at an appropriate epoch.

@@

@@

For each image in the test set, the ``true labels" are nine human-assigned labels of 0 or 1 corresponding to \svp{the presence or absence of} each of the nine shape categories \svp{in the image}. When the CNN predicts which shapes are in the image, however, it assigns a probability between 0 and 1 for each shape category, with a total of nine probabilities per test image. Thus, to determine the accuracy of the model predictions, \svp{fix weird phrasing - we must select a threshold for each label to discretize the model predictions} \fix{one must choose a threshold to the probabilities, such that a predicted probability above the threshold indicates a ``yes" prediction from the model and a probability below the threshold indicates a ``no".} If the threshold is too high, \fix{moderate} probabilities will be treated as a ``no", which increases the number of true negative and false negative predictions. Conversely, if the threshold is too low, \fix{moderate} probabilites will be considered as ``yes", which increases the true and false positive predictions in the data. An appropriate threshold must be chosen to produce a high true positive rate while also ideally keeping the false positive rate low.

Receiver Operating Characteristic (ROC) curves are a type diagnostic plot \svp{which compare} the false positive rate \svp{to} the true positive rate for a classification method.\svp{Make this two sentences so that it's less convoluted}\fix{, computed by comparing the two rates at a number of thresholds, and the Area Under the Curve (AUC) quantifies the shape of the ROC curve.} Perfect prediction would be indicated by a right angle along the upper left corner of the plot, with a corresponding AUC of 1, and a diagonal line with an AUC of 0.5 would indicate that the classification method performs no better than random chance. \autoref{fig:overall-roc} shows the ROC curve for \fix{the model} across all classes, and \autoref{fig:class-roc} shows the curve for each class. The full model has an AUC of 0.88, and the AUC for individual classes ranges from 0.81 (for lines) to 0.91 (for bowtie and text). While the class performances do vary slightly, each ROC curve is the same general shape and performs significantly better than random chance. The points in \autoref{fig:class-roc} represent the equal error rate (EER), which is the threshold where there is equal probability of a false positive or false negative error. \svp{We will use the class-wise EER to set a threshold corresponding to each class, so that }any model prediction with probability above the EER for that shape is considered a positive prediction.

@@

\svp{I'd focus more on the fact that ROC curves are a general summary of the model's performance, but we must also examine the specific cases where the model misclassifies objects to determine if there is a pattern.}
\mt{ROC curves are useful for summarizing the accuracy of model predictions, but they do not indicate which classes are being assigned the false positive or false negative labels when accuracy is not perfect. A confusion matrix is a helpful diagnostic tool to understand which classes are commonly confused for other classes.} A confusion matrix is a \mt{summary of the relationships between} the labels assigned to an image and the labels predicted by the model.

In the confusion matrix presented in \autoref{fig:confusion_matrix}, the values along the diagonal represent the proportion of true positives captured within each category. The off-diagonal values represent the proportion of false positives for each shape pairing; however, since a single image may truly contain multiple shapes, the values \svp{have been} adjusted to remove the effect of any true positives from the calculation of false positive proportions. \svp{I can't remember exactly how we're doing that, but we may want to look more closely at that - if we set everything to NA instead of 0, the rate calculations would be higher than expected}. For example, to calculate the proportion of images that contain triangles but are being falsely labeled as containing quadrilaterals, any image that truly contains both triangles and quadrilaterals is removed before calculating the proportion of false quadrilateral labels.

@@

\autoref{fig:confusion_matrix} shows \svp{systematic errors in class predictions}, but does not necessarily suggest \emph{why} the confusion is taking place. To assess the reasons for model failure, \svp{we look at the images to} \fix{see what the model is seeing.}
%the general weaknesses of the model, but does not necessarily suggest where to look as to \emph{why} the model is not performing appropriately.

>>>>

In this paper, we discuss an alternate approach that uses an additional model layer to transfer the feature vector output into a vector of probabilities representing the detection of geometric elements in shoe tread images. Working within the feature space used by forensic examiners allows us to augment human-identified features with model output, assessing similarity of different shoe images on a feature set that is explicitly relevant to the domain.
In addition, much of the existing software to assess geometric similarity, such as SoleMate\footnote{\url{http://www.fosterfreeman.com/trace-evidence/357-sicar-6-solemate-2.html}}, requires examiners to identify and label features manually; automating classification within the currently used feature space could reduce or eliminate the need for such manual classification.

\section{Materials and Methods}

\mt{Ultimately, most pattern evidence is stored in photographic form; as a result, we must use image analysis methods to create numerical features from the original visual record.} There are a number of methods that may be employed to identify shapes and features in an image, such as Fourier transforms, Hough transformations \citep{ballardGeneralizingHoughTransform1981} and other low-level feature extraction methods aimed at detecting specific shapes, such as edges, corners, blobs, or ridges \citep[Ch 15]{machineVision}. While these methods are useful in identifying these specific features at a low level, they can be computationally intensive and only identify features on a very small scale; as a result, they cannot reliably identify large geometric shapes like those that may be found in an outsole image.

%\svp{Motivate the use of CNNs directly - complex model, higher level of feature aggregation. Mention pre-trained networks to transition.}
Convolutional neural networks (CNNs) are widely recognized as superior for novel image classification. CNNs are a form of artificial neural network which make use of the image convolution operator used by many low-level feature extraction methods, with the additional ability to aggregate such features and meaningfully connect them to a pre-determined set of labels. CNNs have deep architectures that can be trained to identify complex patterns, but they are structurally similar to the architecture of the human visual system and output binary or probabilistic predictions for given labels that are readily interpretable. As CNNs make use of labeled training data, the predictions generated are for features which are similar to those identified by humans, resulting in models with greater face validity. Once a CNN is trained, it is relatively fast and easy to apply the model to new images and obtain classifications.

@@

Many convolutional neural networks have been trained on a set of images known as ImageNet; these images are hierarchically labeled, so the same image of a dog may have labels of sky, grass, and trees, and the dog may be labeled as ``mammal'', ``dog'', ``retriever'', and ``golden retriever'' at increasing levels of label complexity \citep{dengImageNetLargeScaleHierarchical}. CNNs trained on ImageNet are optimized for general human-like vision, that is, the ability to recognize a large set of different features simultaneously. As a result, the base of networks trained on these sets are often used for transfer learning, because the initial layers are broadly generalizable to a wide variety of more specific image labeling tasks.
\svp{You need to talk about the model structure of vgg16 before you start talking about layers. Talk of convolutional blocks doesn't really make sense until you show the layer structure.}
\mt{I agree, but I thought that this was where we were arguing that the ``eyes" are transferrable, so I wanted to talk about the filters to back that up.}
\autoref{fig:vgg16layers} shows a selection of filters from VGG16, where each filter detects the presence of specific shapes and colors. Each row of filters in \autoref{fig:vgg16layers} corresponds to one of the five convolutional blocks of VGG16. Filters in earlier convolutional blocks detect simple features, such as colors and blobs, while later filters detect more complex combinations of features. Each of the five convolutional blocks has between 128 and 1,536 filters, and a single image is made up of some combination of the thousands of features that are detected by those filters.

@@

<<vgg16layers, fig.width = 7, fig.height = 5.75, fig.cap = "A selection of filters from the convolutional layers of VGG16.">>=
imgs <- list.files(file.path(wd, "images", "vgg16layers"),
                   recursive = T, full.names = T)
pngs <- lapply(imgs, function(x) png::readPNG(x)[46:1596, 32:1582, ])
grobs <- lapply(pngs, grid::rasterGrob)
filters <- gridExtra::arrangeGrob(grobs = grobs, nrow = 5)
ggsave(filename = file.path(wd, "images", "unlabeled_filters.png"),
       plot = filters, device = "png", width = 6, height = 5.3)

library(magick)
b <- image_blank(width = 300, height = 1590)
f <- image_read(file.path(wd, "images", "unlabeled_filters.png"))
f_l <- image_append(c(b, f)) %>%
  image_annotate("Block 1:", location = "+60+159",
                 color = "black", size = 60) %>%
  image_annotate("Block 2:", location = "+60+477",
                 color = "black", size = 60) %>%
  image_annotate("Block 3:", location = "+60+795",
                 color = "black", size = 60) %>%
  image_annotate("Block 4:", location = "+60+1113",
                 color = "black", size = 60) %>%
  image_annotate("Block 5:", location = "+60+1431",
                 color = "black", size = 60) %>%
  image_scale(geometry = "600x")
image_write(image = f_l, path = file.path(wd, "images", "labeled_filters.png"),
            format = "png")
knitr::include_graphics(file.path(wd, "images", "labeled_filters.png"))
@

@@

The categories we use in this study are operationally defined as follows:
\begin{description}
\item [Bowtie] Bowtie shapes are roughly quadrilateral, with two opposite concave faces. The remaining two faces can be convex or straight, and the concave faces may have straight portions, so long as there is a concave region. %Using this definition, shapes such as butterflies are included as bowties.
\item [Chevron] Chevron shapes include repeating parallel lines as well as individual ``v" shapes. They may be angular but can also be curved.
\item [Circle] Circles include ellipses and ovals; they must be round.
\item [Line] Lines are repeated and parallel; a more general definition of a line would be difficult to differentiate from many other patterns. Lines can be mildly curved.
\item [Polygon] Polygons are defined in this standard to have more than 4 sides. They include pentagons, hexagons, and octagons.
\item [Quadrilateral] Quadrilaterals (quads) have four sides. They may have rounded or square corners.
\item [Star] Stars are any shape with alternating concave and convex regions, or lines which emanate from a central point. ``X" and ``+" shapes are also classified as stars.
\item [Text] Text is any shape which would be identified as text by a reasonable human. In most cases, the text on the outsole images used is made up of Latin alphabet characters; the model will likely not recognize text in other scripts (but could be trained if non-Latin text images could be obtained).
\item [Triangle] Triangles are any three-sided figure. Like quadrilaterals, they can have rounded corners. In some cases, it is difficult to distinguish between a trapezoidal shape and a triangle when rounded corners are involved.
\item [Other] Other features which were marked include logos, various textures (including crepe, stippling, etc.), and smooth regions with no discernible features. These regions are grouped and provide additional information - that none of the previous nine categories are present. \mt{Why no EM dash? ``---"}
\end{description}

@@

%Labeled images are scarce relative to the amount of data necessary to train a neural network.
Although transfer learning substantially reduces the amount of data required to train a CNN by several orders of magnitude, \fix{labeled images are still difficult or time-consuming to generate relative to the amount of data necessary to train even a small neural network adequately. Another common solution to data scarcity is to artificially enlarge the data set using a process called image augmentation \citep{krizhevskyImageNetClassificationDeep2012}.}
\svp{I would lose the last clause of the first sentence and combine it with the next, e.g. to make most efficient use of the labeled data, we enlarge the training data using a process called image augmentation.}
\mt{I don't think the first half of the first sentence is relevant here without the second. Should I use a different transition? I was trying to put augmentation in the context of transfer learning; i.e., transfer learning helps, but getting data is hard, so we use augmentation to get more, with the added benefit of improving generalizability.}
Augmentation is the transformation of original input data using image operations such as cropping, zoom, skew, rotation, and color balance modification in order to distort or alter the image while maintaining the essential features corresponding to the label. This process reduces the potential for overfitting the model to the specific set of image data used during the training process, and also increases the amount of data available for training. Examples of pre- and post-augmentation images are shown in \autoref{fig:augmented}.

@@

The \Sexpr{nrow(dfunion)} images were split such that 60\% were used for training. Since the categories do not exist in equal proportion in the labeled data,
the training data were weighted by proportion during the training process to ensure that the model can identify both rare and common geometric shapes. Of the remaining 40\% of data, half were used for validation, to monitor the training process, and the remaining data were for testing the performance of the fitted model.

@@

\autoref{fig:training-accuracy} shows the training and validation accuracy and loss at each epoch of the fitting process. Overfitting occurs when a model learns the training data so well that its understanding of the categories becomes specific to the training cases, which, in turn, leads to poor prediction of new images that were not in the training set.
%Overfitting, or fitting a model which performs too well on the training data relative to the validation data,
Overfitting occurs when the validation loss begins to increase after reaching a global minimum. Alternately, underfitting occurs if the validation accuracy is still increasing when model optimization is terminated (for instance, between epochs 1 and 10 in \autoref{fig:training-accuracy}), because model performance is still improving with continued training. In \autoref{fig:training-accuracy}, validation accuracy levels off after epoch 20, and validation loss has not yet begun to increase at epoch 30, indicating that the model optimization process was halted at an appropriate epoch.

@@

\mt{\textbf{OUTLINE OF RESULTS}
\begin{itemize}
\item ROC shows that, in general, model performance is better than chance and broadly compares class performance.
\item Show model predictions primarily to provide a few examples to back up the claim that predictions generally look good, but also include one or two case studies that motivate class-by-class diagnostics
\item Confusion matrix shows which classes are most accurate or most problematic. However, when we see that one shape is commonly misclasified as another, the conf mat doesn't let us do anything more than speculate the cause.
\item Heatmaps help us look at specific instances of classification to 1) verify that the model is using appropriate features when it classifies correctly and 2) diagnose the cause of confusion when the model classifies incorrectly
\item (Potentially switch the order of prediction examples and the confusion matrix, so the conf mat indicates systemic class confusion and then back that up with the examples?)
\end{itemize}
}

@@

For each image in the test set, the ``true labels" are nine human-assigned labels of 0 or 1 corresponding to \svp{the presence or absence of} each of the nine shape categories \svp{in the image}. When the CNN predicts which shapes are in the image, however, it assigns a probability between 0 and 1 for each shape category, with a total of nine probabilities per test image. Thus, to determine the accuracy of the model predictions, we must select a threshold for each label to discretize the model predictions. %such that a predicted probability above the threshold indicates a ``yes" prediction from the model and a probability below the threshold indicates a ``no".}
If the threshold is too high, \fix{moderate} probabilities will be treated as a ``no", which increases the number of true negative and false negative predictions. Conversely, if the threshold is too low, \fix{moderate} probabilites will be considered as ``yes", which increases the true and false positive predictions in the data. An appropriate threshold must be chosen to produce a high true positive rate while also ideally keeping the false positive rate low.

%\mt{I don't immediately see how to separate the below sentence into two without making it really clunky... I figured that in the context of thresholds (previous paragraph), it would be easy to just stick in that those thresholds are used to compute the curve.}

%Better?: Receiver Operating Characteristic (ROC) curves are a type diagnostic plot which compare the false positive rate to the true positive rate for a classification method at a number of thresholds, and the Area Under the Curve (AUC) quantifies the shape of the ROC curve.

Receiver Operating Characteristic (ROC) curves are a type diagnostic plot which compare the false positive rate to the true positive rate for a classification method.\svp{Make this two sentences so that it's less convoluted}\fix{, computed by comparing the two rates at a number of thresholds, and the Area Under the Curve (AUC) quantifies the shape of the ROC curve.} Perfect prediction would be indicated by a right angle along the upper left corner of the plot, with a corresponding AUC of 1, and a diagonal line with an AUC of 0.5 would indicate that the classification method performs no better than random chance. \autoref{fig:overall-roc} shows the ROC curve for \fix{the model} across all classes, and \autoref{fig:class-roc} shows the curve for each class. The full model has an AUC of 0.88, and the AUC for individual classes ranges from 0.81 (for lines) to 0.91 (for bowtie and text). While the class performances do vary slightly, each ROC curve is the same general shape and performs significantly better than random chance. The points in \autoref{fig:class-roc} represent the equal error rate (EER), which is the threshold where there is equal probability of a false positive or false negative error. We will use the class-wise EER to set a threshold corresponding to each class, so that any model prediction with probability above the EER for that shape is considered a positive prediction.

@@

\svp{I'd focus more on the fact that ROC curves are a general summary of the model's performance, but we must also examine the specific cases where the model misclassifies objects to determine if there is a pattern.}
\mt{ROC curves provide a general summary of model accuracy, but they do not indicate which classes are being assigned the false positive or false negative labels when accuracy is not perfect. A confusion matrix is a helpful diagnostic tool to understand which classes are commonly confused for other classes.} A confusion matrix is a \mt{summary of the relationships between} the labels assigned to an image and the labels predicted by the model.

In the confusion matrix presented in \autoref{fig:confusion_matrix}, the values along the diagonal represent the proportion of true positives captured within each category. The off-diagonal values represent the proportion of false positives for each shape pairing; however, since a single image may truly contain multiple shapes, the values have been adjusted to remove the effect of any true positives from the calculation of false positive proportions. \svp{I can't remember exactly how we're doing that, but we may want to look more closely at that - if we set everything to NA instead of 0, the rate calculations would be higher than expected} \mt{They're being set to NA, and then we're calculating proportions with na.rm = T. I don't understand what you mean about higher rates than expected...}. For example, to calculate the proportion of images that contain triangles but are being falsely labeled as containing quadrilaterals, any image that truly contains both triangles and quadrilaterals is removed before calculating the proportion of false quadrilateral labels.

@@

\autoref{fig:confusion_matrix} shows systematic errors in class predictions, but does not necessarily suggest \emph{why} the confusion is taking place. To assess the reasons for model failure, we look at the images to \fix{see what the model is seeing.}
